Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-16 paper/paper.tex
Iterate Read-Only Transactions

\subsection{Read-Only Transactions \tbr}
\label{subsec:read-only-transactions}

@@

In general, read-only transactions involve group leaders and they may also involve
any other replica which is sufficiently up-to-date. Group leaders are involved
in the negotiation phase. In this phase, all involved Paxos groups negotiate in
order to determine $s_{read}$. To accomplish this, Spanner requires every
read-only transaction to define a \emph{scope} expression which summarizes all
keys that will be read by the respective transaction.

If all values of the scope can be served by a single Paxos group, the client
issues the read-only transaction to the corresponding group leader. The group
leader then assign the timestamp of the last committed write to $s_{read}$ and
executes the transaction.

If serving the values of the scope involves multiple Paxos groups, Spanner avoids
a negotiation round (which would be one viable options). Instead, Spanner simply
assigns$TT.now().latest$ to $s_{read}$, even though this may have to wait for
$t_{safe}$ to advance.

In both cases, the snapshot read executed at $s_{read}$ can execute on any
replica. The leader replicas are only involved in the negotiation phase.

>>>>

\subsection{Read-Only Transactions}
\label{subsec:read-only-transactions}

@@

In general, read-only transactions involve group leaders but they may also involve
any other sufficiently up-to-date replica in the process. Group leaders are
involved in the negotiation phase. In this phase, all involved Paxos groups
negotiate in order to determine $s_{read}$. To accomplish this, Spanner requires
every read-only transaction to define a \emph{scope} expression which summarizes
all keys that will be read by the respective transaction.

If all values of the scope can be served by a single Paxos group, the client
issues the read-only transaction to the corresponding group leader. The group
leader then assigns the timestamp of the last committed write to $s_{read}$ and
executes the transaction.

If serving the values of the scope involves multiple Paxos groups, Spanner avoids
a negotiation round (which would be a viable option). Instead, Spanner simply
assigns $TT.now().latest$ to $s_{read}$, even though this may have to wait for
$t_{safe}$ to advance.

In both cases, the snapshot read at $s_{read}$ can execute on any sufficiently
up-to-date replica. The leader replicas are only involved in the negotiation
phase.
